\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Brock Ellefson}
\title{WRIT221 Abstract Translation}
\begin{document}

\maketitle

\section*{Original Text}

Education costs, especially textbook prices, are outpacing inflation and becoming a serious financial
burden for college students. Because student textbook use is linked to academic performance,
making textbooks more affordable and accessible is one important way to enhance learning outcomes.
Online booksellers allow student-to- student textbook sales, which can lead to substantial savings for
students. This study demonstrates that the prices of used science textbooks on Amazon.com
demonstrate a clear supply-and- demand pattern, with prices increasing at the beginning of a semester
when supply is low and falling at the end of the semester when supply is high. We show that students
can save 20-33 on science textbooks by timing online textbook purchases carefully. We estimate
savings of 452 over the course of a 4-year college degree by purchasing textbooks early. To enable
students to save on science textbook purchases, we suggest that instructors notify registered students
of the required course materials during the class registration period (near the end of the semester
preceding the class). Such savings can greatly improve the affordability and accessibility
of textbooks for students, which may lead to enhanced learning.

\section*{Facebook Post}
%40 words
Thank god for online student to student textbook sales, I saved like 450 bucks after graduation! The prices that Montana State charges is way too much, I a broke college student, how am I supposed to afford a \$200 textbook? 

\section*{Tweet}
%140 Characters
Yo I got the CS101 textbook for sale on studentsales.com for \$40 bucks.\$\$\$ \#financialwizard. 

\section*{Website Copy}
%200 Word Recreation
Textbook prices are beginning to get out of hand. Many college students can't even afford some or all of their textbooks. Obviously, students who have their textbooks are going to have a better knowledge of the material and a better grade than the average student without a textbook. Clearly, this is a problem that needs to be addressed. Right now, the current strategy is to actually go around the college bookstore and either order textbooks online or from another student at a highly discounted price. Towards the end of the semester, professors should should notify students who plan to take the course the following semester of all the materials needed. This advance will give students who already took the class time to sell their textbooks to upcoming students taking the class at an affordable price. Overall this should create not only a better economy to purchase books and generate a whole new batch of students that will better understand the material, leading to better grades. 

\section*{Analysis}

I tried my best to 

\end{document}