\documentclass[a4paper,12pt]{letter}

% Some of the article customisations are relevant for this class

\author{Brock Ellefson} % To be used for the return address on the envelope


\makelabels % this command prints envelope labels on the final page of the document

\begin{document}

Dear ID Tech\\\\
My name is Brock Ellefson, I saw your listing for instructors for your summer programming camps and I am very interested in your  programming instructor position. Mentoring children is something I enjoy and having the opportunity to help them understand and enjoy computing would change their lives and being a part of that would be incredible. \\ 


This is currently my third year studying Computer Science at Montana State University. Despite being an undergraduate, I have a lot of experience in programming. I am not the next Bill Gates nor Vint Cerf however I am very passionate about computer science, constantly pushing myself to expand my knowledge of coding. I programmed my first 2D game from scratch on Blitz Basic. It was complete with sprites as well as custom-made sounds. Right now I'm in the process of independently developing my first android app, GroupEffort, in my spare time. I possess a lot of patience when it comes to working with kids, not only was I a mentor for freshmen in high school, but I have also been a youth soccer coach for a brief time. Being a computer salesmen for Staples, I gained a lot of customer service experience selling software and answering any inquires a customers has.\\   

An old boss of mine Samuel Quick, a network administrator, always thought merging my talented people skills with my knowledge of programming would be the best course for me. Hopefully you consider me a qualified applicant. Attached is my resume, feel free to contact me via cell phone or email. I look forward to hearing from you.

Thank you for your time, \\
Brock
\end{document}
