\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{setspace}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{times}
\usepackage{setspace}
\author{Brock Ellefson}
\title{CSCI432 P6 Individual}
\begin{document}
\maketitle
\doublespacing
For this project, I created the entire video, what it would contain, the style and direction, and script. I structured how the presentation would go, I also created the visualization part of the +1 as well as comparing Introsort to the other sorting algorithms. Our biggest strength in our project was our presentation in my opinion. I felt like most of the class was engaged in conversion and we convoked the most discussion out of any group. That being said our group had massive issues. I honestly felt like Seth Severa and I were the only ones that did anything. Team members rarely texted me back to meet up or work on the project. There was even a time where I texted the group chat and I didn't get a single response until 26 hours later, I was pretty upset about that. I really feel like I did a massive part of the project while the other did almost nothing. Mitch Baker never responded to any text messages and did not contribute to anything for deliverable 5 or 6. Seth and I were the only ones that worked on deliverable 5 and 6 papers. Alex and Yue created the c++ file, however they did not communicate that they were even working on it at all. Obviously our biggest weakness was communication between one another. Overall, I was very frustrated with my group members and if I could do it again I would pick more trustworthy members.

\end{document}